The Transition from Massive Metal Free Stars to Dwarf Galaxies

### 2011-02-09 ms.tex
Adding halo details and arXiv numbers to references.

Fig. \ref{fig:ztot} quantifies the fraction of haloes at a given mass
are enriched above a mean total metallicity [Z/H] = --3, --4, and --5
at redshifts 7, 8, 10, and 12.  The minihaloes with $M \sim 10^6$ are
primarily enriched by PISNe and are nearly equal to the metal volume
filling fraction, shown in Fig. \ref{fig:z3fill}, for all metallicity
cuts.  The fraction linearly increases to approximately 0.6 for [Z/H]
= --3 and 0.8 for the [Z/H] = --4 and --5 cuts at a halo mass of
\tento{7}\Ms because these larger haloes have a higher probability
that one of its progenitors hosted a PISN.  For the lower two
metallicity cuts, the fraction continues to increase until all of the
haloes are enriched above $3 \times 10^7 \Ms$ and $10^8 \Ms$ for [Z/H]
= --4 and --5, respectively.  These trends are redshift independent
for the data shown here because the halo mass (with respect to the
filtering mass) is driving factor in controlling star formation and
metal production.  For the metallicity cut of [Z/H] = --3, there is
considerable noise from redshift to redshift.  But at redshift 7, all
of the haloes above \tento{8}\Ms are enriched above this level except
for Halo 2 (there are only 2 halos in the $2 \times 10^8 \Ms$ bin),
because it hosts too little star formation for significant
self-enrichment to occur.

@@

\halo{0}

\halo{1}

\halo{2}

\halo{3}

\halo{4}

\halo{5}

\halo{6}

\halo{7}

\halo{8}

\halo{9}

>>>>

Fig. \ref{fig:ztot} quantifies the fraction of haloes at a given mass
are enriched above a mean total metallicity [Z/H] = --3, --4, and --5
at redshifts 7, 8, 10, and 12.  The minihaloes with $M \sim 10^6 \Ms$
are primarily enriched by PISNe and are nearly equal to the metal
volume filling fraction, shown in Fig. \ref{fig:z3fill}, for all
metallicity cuts.  The fraction linearly increases to approximately
0.6 for [Z/H] = --3 and 0.8 for the [Z/H] = --4 and --5 cuts at a halo
mass of \tento{7}\Ms~because these larger haloes have a higher
probability that one of its progenitors hosted a PISN.  For the lower
two metallicity cuts, the fraction continues to increase until all of
the haloes are enriched above $3 \times 10^7 \Ms$ and $10^8 \Ms$ for
[Z/H] = --4 and --5, respectively.  These trends are redshift
independent for the data shown here because the halo mass (with
respect to the filtering mass) is driving factor in controlling star
formation and metal production.  For the metallicity cut of [Z/H] =
--3, there is considerable noise from redshift to redshift.  But at
redshift 7, all of the haloes above \tento{8}\Ms~are enriched above
this level except for Halo 2 (there are only 2 halos in the $2 \times
10^8 \Ms$ bin), because it hosts too little star formation for
significant self-enrichment to occur.

@@

\halo{3} Fig. \ref{fig:Zevo} shows that metal enrichment from Pop II
stars occurs 10 Myr after a PISN.  In this case, PISN remnant did not
escape from the halo \citep[cf.][]{Whalen08_SN}, leaving the halo
metal-enriched and relatively gas-rich.  This gas later formed 3000
\Ms~of Pop II stars in two stellar clusters with very different
metallicities of [Z/H] = --3.5 and --1.2 seen in Fig. \ref{fig:SFH}.
Because this triggered star formation was weak, it does not
significantly enrich further, only reaching a metallicity of $\ztwo
\sim -4.5$ before the galaxy hosts a starburst at $z = 9.5$.

\halo{4} A nearby minihalo initially enriched the most massive
progenitor, triggering Pop II star formation without hosting a Pop III
star at $z=15$ when the halo mass was only $5 \times 10^6 \Ms$.  This
halo experiences a series of major and minor mergers at $z > 10$ and
very little afterwards.  The lack of mergers allows a gas and stellar
disc to form, unlike all of the other galaxies in the simulation.  SNe
feedback creates a bipolar outflow, perpendicular to the disc, that
enriches the surrounding IGM but not the halo itself.

\halo{7} Triggerred star formation similar to Halo 3 occurs in this
halo, where the PISN does not expel the majority of the gas.  2000
\Ms~of stars form in the expanding SN remnant shell, promptly
enriching the halo shortly after the PISN, shown in
Fig. \ref{fig:Zevo}.  Because these stars formed in the reference
frame of the expanding shell, they escape from the halo, only
enriching the halo to $\ztwo \sim -4.5$.  These stars never return to
the halo and are still located in the IGM at $z=7$.

\halo{8} This halo resides 4.5 kpc from Halo 0 at $z=7$ and is
subjected to strong UV radiation that suppresses all star formation
even after it becomes gas rich with $f_g > 0.1$ at $z \la 8$.
